Volatility and the Buyback Anomaly

### 2016-04-25 bb_issuers_new.Rnw
new version

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#dev.off();
#library(knitr); knit2pdf('bb_issuers_new.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers_new",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx

@@

@@

\title{Share Buyback and Equity Issue Anomalies Revisited}%\footnotetext{}

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high, and not significant otherwise. This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks. The results hold for both small and large firms. We also find no post-equity issue abnormal returns when using the five-factor model proposed by Fama and French (2015a). However, the post-buyback announcement abnormal returns are also higher for firms that subsequently announce an equity issue. Finally, based on our findings we extend the Undervaluation Index of \citep{PeyerVermaelen2009}.  
\end{abstract}
\vspace{2cm}

@@

The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program. Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}. What makes these capital structure anomalies different so that they stand the test of time?

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}. If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}. Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

@@

The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios. We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.

The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e. (idiosyncratic) volatility is negatively related to expected returns. For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.  So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}. If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.

Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

This paper is organized as follows. In section 2 we describe our data. In section 3 we test whether buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model. We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently. In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry. In section 5 we test whether idiosyncratic risk as well as volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}. Section 6 concludes.

@@

Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A. Our results are largely consistent with \cite{FamaFrench2015b}. Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}). However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months. This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure. Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time. Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results. Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement. Actual repurchase dates thus do not correspond to announcement dates. Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.

@@

@@

Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model. Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

\subsection{Robustness across Sectors}
\label{sec:AllIndustries}

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
@

Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software and semiconductor industries are the most active repurchasers. They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}. Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).  Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.  So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed. For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline. This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns. However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.  Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.

@@

The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \citep{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks.  Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).  So our results are also consistent with the \cite{Stambaugh2015} interpretation.

\subsection{Volatility}
\label{sec:volbuybacks}

>>>>

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#dev.off();
#library(knitr); knit2pdf('bb_issuers_new.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers_new",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# system("pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")

@@

if (0){ # To add later
  qfactors <- read.csv("dataset/indices_and_factors/qfactors.csv", sep=";", dec=".")
  rownames(qfactors) <- paste(qfactors[,1],ifelse(str_length(qfactors[,2]) == 2, qfactors[,2], paste("0",qfactors[,2], sep="")), sep="-")
  useonly = which(rownames(qfactors) %in% str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))
  qfactors = qfactors[useonly,]
  rownames(qfactors) <- rownames(Risk_Factors_Monthly)[match(rownames(qfactors), str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))]
  qfactors = qfactors[,3:6]
  qfactors = apply(qfactors,2,function(r) as.numeric(str_replace(r,",",".")))
  qfactors = qfactors/100
  qfactors = cbind(qfactors,Risk_Factors_Monthly[,c("SMB", "HML","RF","RMW","CMA")])
  formula_used="(ri - RF) ~ MKT + HML + ME + I.A + ROE"
  qfactors_irats_MKT_HML_ME_IA_ROE = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly, BUYBACK_DATA$DATASET$SDC$Event.Date, qfactors, formula_used = formula_used)$results
  qfactors_irats_MKT_HML_ME_IA_ROE = qfactors_irats_MKT_HML_ME_IA_ROE[reported_times,]

}

@@

\title{Volatility and the Buyback Anomaly}%\footnotetext{}

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement volatility and idiosyncratic volatility is high, and not significant otherwise. This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks as well with the prediction that a repurchase authorization is an option to take advantage of undervalued stock prices \citep{IkenberryVermaelen1996}. We also confirm that the buyback anomaly survives  when using the five-factor model proposed by Fama and French (2015a).  Combining volatility with idiosyncratic volatility with other indicators of undervaluation proposed by \citep{PeyerVermaelen2009} improves the predictive power of long term excess returns after buyback anouncements.
\end{abstract}
\vspace{2cm}

@@

The first purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e. the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.} and the volatility anomaly, i.e. the fact that (idiosyncratic) volatility is negatively related to expected returns \cite{Ang2006}. This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses for undervalued stocks\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}, i.e. for undervalued stocks there is a positive relation between idiosyncratic volatility and future returns. They argue that their result is consistent with their costly {\it arbitrage hypothesis}: idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing. So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced. It should be noted that in the volatility literature idiosyncratic volatility is estimated by residual variance of of an asset pricing model such as the Fama-French three factor model. Empirically there is a very high correlation between residual variance and total variance (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) so for the remainder of this paper we will refer to this hypothesis as the volatility anomaly.

As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation), we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue).  Another reason for expecting a positive relation between volatility and future returns after buyback authorization announcements is provided by \cite{IkenberryVermaelen1996}'s {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks. If markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility. Note that this option hypothesis makes no predictions about excess returns after equity issues, unlike buyback authorizations, are firm commitments, not options.  Because residual variance is highly correlated with total volatility, we use an alternative measure of idiosyncratic volatility that is not correlated with volatility: $1-R^2$. It measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information. As the market timing hypothesis (e.g., \cite{IkenberryLakonishokVermaelen1995}) assumes that managers exploit company-specific information it predicts that buyback announcements of firms with high idiosyncratic volatility will generate higher long term excess returns.

However, before proceeding with examining the link between anomalies, it is important to verify that these anomalies are real and not simply a proxy for risk, or have disappeared in recent years as has happened with many other anomalies~\citep{McLean2016}. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that many anomalies are weakened or  do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}. They find that the volatility anomaly survives for small firms, but the net issue anomaly does not. If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}. Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm. So before concluding that the buyback and equity issue anomalies have disappeared, they have to be examined separately, using announcement dates.

So the second major purpose of this paper is to verify whether the buyback and equity issue anomalies still exist using the more recent \cite{FamaFrench2015a} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015a} leads to the same conclusions.} We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}. It remains a fact though that the buyback anomaly is a small firm anomaly: value-weighting all the events (as suggested by~\cite{MitchellStafford2000}) makes the alphas disappear.  So the anomaly does not challenge the view that 99$\%$ of all stocks may well be priced efficiently. It simply shows that small cap firms are priced less efficiently and can take advantage of undervaluation, at least on average. Moreover, while we do not value-weight the events, as argued by \cite{PeyerVermaelen2009}, if anything, to increase the power of the test to detect mispricing, any weighting should be based on the inverse of size.

@@

After having established that the buyback anomaly survives the Fama-French five factor model, we test for the relation between volatility measurers and long term excess returns.  We find a significant {\it  positive} relation between excess returns and volatility as well as idiosyncratic volatility measured by $1-R^2$. Note although there is a high correlation (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) between total volatility and residual variance (the proxy used in the literature for idiosyncratic volatility), the correlation between standardized idiosyncratic volatility and total volatility is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.  The positive relation between $1-R^2$ and excess returns is consistent with the {\it information advantage hypothesis}: in firms with high standardized idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The positive correlation between volatility and excess returns is consistent with the costly arbitrage hypothesis of~\cite{Stambaugh2015} as well as with the option hypothesis of~\cite{IkenberryVermaelen1996}.

Combining  idiosyncratic volatility  and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months. However the strong negative correlation between size and alpha may explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.

In order to address the issue of size (which suggests the buyback anomaly is not economically important), we close with a section on buyback anomalies for large firms. We find that there is a buyback anomaly for large firms, but only if we focus on large volatility stocks. This suggests that when there is large uncertainty about fundamental value, even in large firms the option to repurchase stock at prices below fair value is worth a lot. Note however that the alpha for these large high volatility firms is significantly smaller than the alpha of the high Enhanced undervaluation index so there remains a tradeoff between excess returns and firm size.

This paper is organized as follows. In section 2 we describe our data. In section 3 we test whether buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model. We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently. In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry. In section 5 we test whether  idiosyncratic risk as well as total volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}. Section 6 concludes.

@@

Table~\ref{tbl:priorIssuers}, Panel~A, shows the results for all equity issues, using the same methodology as in Table~\ref{tbl:priorBuybacks}, Panel~A. Our results are largely consistent with \cite{FamaFrench2015b}. Using the three-factor model, we find statistically significant long term (after 48 months) negative cumulative excess returns of \Sexpr{IRATS_table_all_iss["+48","CAR 3F"]}$\%$ (t=\Sexpr{IRATS_table_all_iss["+48",2]}). However, once we use the five-factor model as a benchmark, excess returns fall and become statistically insignificant after 48 months. This indicates that when searching for anomalies, buybacks and equity issues should not be pooled in a ``net issue'' measure, a habit unfortunately adopted by numerous authors. Unlike buybacks, equity issues are firm commitments and announced and completed at the same point in time. Using actual shares issued, the measure used by \cite{FamaFrench2015b}, and equity announcements (our measure) should therefore produce similar results. Buyback authorization announcements on the other hand are not firm commitments and are often executed over a long period after the announcement. Actual repurchase dates thus do not correspond to announcement dates. Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss[reported_times[1],1],0)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement negative excess returns shows that this was not reflecting ``irrational exuberance'' but rather that these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them.

@@

So far all our events are equally weighted. \cite{MitchellStafford2000} argue that events should be value weighted to test whether represent an economically important anomaly. However, as we know from past research, for theoretical as well as empirical reasons, one would expect that managers in small firms are better able and willing to take advantage of mispricing than in large firms. So value weighting would simply bias the results toward zero. And indeed, when we value-weight the events (results available upon request) long-term excess returns become statistically insignificantly different from zero. So the buyback anomaly is not economically important and does not challenge the basic premise that ``the market'' represented by a value-weighted index is priced correctly.

@@

%Figure~\ref{fig:pastall} summarizes the IRATS results in more detail by showing the cumulative abnormal returns during the 6 month pre and 48 month post event period, using the five-factor model. Results are shown for the total sample of buybacks and equity issues, as well as for high and low U-index buyback samples.

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} allows us to verify that the excess returns are not simply the result of outperformance during a particular time period. %Table~\ref{tbl:allhedgedBB} shows the monthly and yearly returns of this five-factors hedged strategy for N=12.  The table shows that in \Sexpr{sum(tmp[,13] > 0)} of \Sexpr{sum(tmp[,13] != 0)} years the excess returns are positive, with a large \Sexpr{round(max(tmp[,13]),1)}$\%$ excess return in  \Sexpr{rownames(tmp)[which.max(tmp[,13])]}. In only one year (\Sexpr{rownames(tmp)[which.min(tmp[,13])]}) the strategy generates an abnormal loss larger than \Sexpr{round(abs(sort(tmp[,13])[2]),1)}$\%$.

%\subsection{Robustness across Sectors}
%\label{sec:AllIndustries}

%<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
%tmp = Reduce(cbind,lapply(1:length(industry_BB), function(i) industry_BB[[i]][,1:3] ))
%@

%Figure~\ref{fig:industryeventsBB} shows the number of buyback events per industry in our sample. The software and semiconductor industries are the most active repurchasers. They also tend to be the most volatile industries, industries where disagreement about fundamental value is large - as we report later in Table \ref{tbl:industriesR2Vol}. Table~\ref{tbl:IndustriesBB} shows the IRATS cumulative abnormal returns and Table~\ref{tbl:IndustriesBB_cal} the Calendar Time method monthly average abnormal returns when we remove one industry at the time, for the top most frequent buyback industries (those for which there are at least \Sexpr{min_industry_sampleBB} events in our sample).  Note from Table~\ref{tbl:priorBuybacks} that, after 48 months, the cumulative abnormal returns for the whole sample (using IRATS) is \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ and the monthly average excess return (Calendar Time) is \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$.  So the larger the difference between these numbers and the corresponding numbers for the industry indicated in Tables~\ref{tbl:IndustriesBB} and \ref{tbl:IndustriesBB_cal}, the larger the excess returns in the industry removed. For example, using IRATS, deleting the software industry lowers the CAR from \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ to \Sexpr{round(tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$, a \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"] - tmp["+48", 3*(which(names(industry_BB) == "Software")-1)+1],2)}$\%$ decline. This is the largest decline in Table~\ref{tbl:IndustriesBB}, indicating that buybacks in the software industry are followed by the largest excess returns. However, deleting Retail, Insurance, Machinery, Meals and especially Chemical stocks improves the excess returns.  Of course, these differences could be explained by differences in U-index levels or other indicators of the likelihood of misvaluation, a topic we turn to next.

@@

%The finding that $1-R^2$ and idiosyncratic volatility (IVOL in \citep{Ang2006}, measured as the standard deviation of the residuals of the factor model regression) are positively related to future excess returns is inconsistent with \cite{Ang2006} who find a negative relation between IVOL and expected returns. However, \cite{Stambaugh2015} argue that the relationship between IVOL and returns becomes positive for undervalued stocks. Their argument is that IVOL represents risk that deters arbitrage and therefore creates mispricing. Using a proxy for mispricing based on 11 anomalies they find indeed a positive relation between IVOL and future returns for undervalued stocks. Their most under-priced high IVOL stocks earn monthly excess returns (relative to the Fama-French three-factor model) of 0.56$\%$ per month which is quite similar to the \Sexpr{R2_IRATStableBB_cal["+48","High Idiosync.: CAL"]}$\%$ per month reported in our Table~\ref{tbl:IdiosyncraticunderBB} Panel B (using the five-factor model).  So our results are also consistent with the \cite{Stambaugh2015} interpretation.

\subsection{Volatility and excess returns}
\label{sec:volbuybacks}
